\documentclass[11pt,a4paper]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\signature{Josie Taranto}
\address{6/676 Mount Albert Road\\ Auckland, New Zealand}

\begin{document}

\begin{letter}{Hiring Manager\\ Towing And Recovery Ltd\\ 24 Paramount Drive\\ Henderson, Auckland}

\opening{Dear Hiring Manager,}

As someone who has always thrived in fast-paced, client-focused environments, I was excited to come across the Office Support / Front Receptionist position at Towing And Recovery Ltd. Your company's reputation for reliable and professional towing services resonates with my own commitment to excellence in customer care.

My journey from Brazil to New Zealand has taught me the value of adaptability and clear communication – skills I believe are crucial in the towing industry where every call could be an emergency. In my current role at Bonita Brazilian Beauty, I've become adept at:

\begin{itemize}
    \item Juggling multiple priorities while maintaining a calm demeanor – a skill I imagine is vital when coordinating towing assignments.
    \item Turning potentially stressful situations into positive experiences for clients – something I'm sure your customers appreciate during vehicle breakdowns.
    \item Streamlining administrative processes, which I believe could help in managing service orders and billing information efficiently.
\end{itemize}

What intrigues me most about this role is the opportunity to be the first point of contact for people who might be having a challenging day. I see it as more than just answering phones or scheduling services; it's about providing reassurance and solutions to people in need.

My background in graphic design has honed my attention to detail and problem-solving skills. I'm excited about the possibility of applying these skills to maintain meticulous records and perhaps even contribute ideas to improve visual communications within the company.

I'm eager to bring my unique blend of experiences to Towing And Recovery Ltd and to learn the intricacies of the towing industry. I'd love the opportunity to discuss how my skills could contribute to your team's success and to learn more about the challenges and rewards of this role.

Thank you for considering my application. I look forward to the possibility of joining your team and helping to keep Auckland moving.

\closing{Warm regards,}

\end{letter}
\end{document}